
\documentclass[letterpaper,twocolumn,10pt]{article}
\usepackage{usenix,epsfig,endnotes}
\usepackage{color}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage[noend]{algorithmic}
\usepackage{graphicx,subfigure}
\DeclareGraphicsExtensions{.eps,.ps,.eps.gz,.ps.gz,.eps.Z}
\usepackage{stfloats}

\begin{document}

%don't want date printed
\date{}

%make title bold and 14 pt font (Latex default is non-bold, 16 pt)
\title{\Large \bf START: Status and Region Aware Taxi Mobility Model for Urban Vehicular Networks}

%for single author (just remove % characters)
\author{
{\rm Haiquan Wang\thanks{
 This research has been partially supported by the US National Science Foundation (NSF) under Grant No. CNS-1319915 and CNS-1343355, the National Natural Science Foundation of China (NSFC) under Grant No.61300173 and No. 61170295, the Project of Aeronautical Science Foundation of China under Grant No.2013ZC51026 and No.2011ZC51024, the Fundamental Research Funds for the Central Universities under Grant No. YWF-12-LXGY-001, and the State Key Laboratory Software Development Environment and Network Information and Computing Center of Beihang University.}}\\
{\rm Wenjing Yang}\\
{\rm Jingtao Zhang}\\
{\rm Jiejie Zhao}\\
School of Software, Beihang University, Beijing, P.R.China\\
Beijing Key Laboratory of Network Technology, Beijing, P.R.China
\and
{\rm Yu Wang*}\\
Department of Computer Science, University of North Carolina at Charlotte, Charlotte, NC, USA\\
corresponding author
% copy the following lines to add more authors
% \and
% {\rm Name}\\
%Name Institution
} % end author

\maketitle

% Use the following at camera-ready time to suppress page numbers.
% Comment it out when you first submit the paper for review.
\thispagestyle{empty}


\subsection*{Abstract}
Using a realistic mobility model will enhance the validity of simulations, while the difficulty lies in discovering rules from large amounts of data and applying those rules. Researchers have been working on mobility model extracting from real data set, whereas the taxi behavior difference between different taxi statuses was ignored in previous works. As statistical analysis results of real taxi traces demonstrate certain distribution law of speed and duration for each status and geographical features, a novel taxi movement model START is proposed with respect to taxi statuses and regions. Micro-scope and macro-scope are both considered. In micro-scope, speed and duration cumulative distribution are fitted to estimate the speed of node and the node¡¯s duration in corresponding status. And in macro-scope, a transition probability matrix is calculated to define the node¡¯s movement from region to region. Instead of simply dividing the area into squares, we cluster the squares with higher taxi dense quantity and define two types of regions -- dense region and sparse region.  Simulations are carried out to display the trace generated by our model to compare the similarity of generated trace features and contact characteristics.
In order to verify our assumptions that the taxi statuses affect the accuracy of models, a simplified movement model S-START based on START is implemented, but it ignores the taxi statuses. The relevance of START, S-START, ShortestPathMovement (based on the map of Beijing) and Random Way Point model with real trace are compared. The simulation results illustrate that the taxi statuses and geographic characteristics have obvious influence on the accuracy of models and the proposed mobility model has a good approximation with reality.


\subsection*{keyword}
mobility model, taxi status, Markov process, dense region, sparse region

\input{file_introduction}

\input{file_related_works_v2}

\section{Assumptions and Statical analysis of Taxi Trace}
\label{section_assumptions_anlysis}

In this section, we mainly focus on statistical analysis on the speed and duration characteristics on the data set.
Firstly, the data set will be introduced in section \ref{section_trace_data}. Then, two assumptions are proposed and validated in the following section \ref{section_statistic_analysis}.

\input{file_trace_dataset}

\subsection{Assumptions and Statistical Analysis of Taxi Data}
\label{section_statistic_analysis}

According to experience in daily life, the following two assumptions are given:

\begin{itemize}
  \item \textbf{Assumption 1:}The behavior of a taxi will change when its status changes. When a taxi is taking passengers, its destination is fixed, and the speed of it is relatively faster. In contrast, when a taxi is vacant, it will slow down or even stop to search for potential passengers along the road. Thus, taxi behavior characteristics, such as speed and the status duration varies consequently.
    
  \item \textbf{Assumption 2:} The movement behavior of taxies associates with geographic feathers.
      \begin{enumerate}
        \item The destination selection will be influenced by different regions.
        \item xxxx
      \end{enumerate}
\end{itemize}
   
   Therefore, we analysis the speed ,duration and load/drop-passenger events distribution to estimate our assumptions.  
   
\input{file_speed_statics}

\input{file_lasting_time_for_each_status}

\input{file_taxi_density_distribution}

\section{Modeling}
\label{section_modeling}
\input{file_model_design}

\input{file_matrix_of_transition_probability}

\input{file_speed_modeling}

\input{file_lasting_time_modeling}


\input{file_evaluation}

\section{Conclusion}
\label{section_conclusion}
Since the mobility model is essential for mobile network, a novel mobility model START based on real GPS trace data is proposed. By assuming the taxi behavior is related with its statuses and taxi distribution in area is uneven, statistical experiments are conducted to verify those assumptions using the real trace data. Further, its parameter--speed and duration in each status are estimated respectively, and the one step transition probability matrix is calculated. In this case, macroscopic (from one region to another) movement and microscopic movement(speed and duration for each status) can be defined. Finally, the START is implemented on ONE simulator and estimate it by comparing with the real trace, RWP and Shortest Path movement Model. A simplified model, S-START, based on START is created, which modifies the parameters of speed distribution, and sets the parameters according to the speed distribution of each status. By comparing the START and the S-START, it can come to the conclusion that the taxi behavior in different status influences the node distribution and contact characteristics. In return, it proves our $assumption$ 1.

Shortest Path movement Model, based on the real map of Beijing and the Dijkstra algorithm, reflects the road structure of the city better than START. However, comparing the node distribution and contact feathers, START shows better performance. Shortest Path movement model takes geographic feathers into consideration, but it neglects uneven geographic distribution. RWP also disregards this feather. Those simulation results above validate the $assumption$ 2 in certain degree.

Simulation results demonstrate that START has a good approximation with reality.


\bibliographystyle{acm}

\bibliography{vehicle_mobility_model}

\end{document}
\endinput




