
%\documentclass[camera-ready,twocolumn,10pt]{IEEEtran}
\documentclass[10pt,conference,compsocconf,letterpaper]{IEEEtran}
\IEEEoverridecommandlockouts

\usepackage{epsfig,endnotes}
\usepackage{color}
\usepackage{amssymb}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx,subfigure}
\DeclareGraphicsExtensions{.eps,.ps,.eps.gz,.ps.gz,.eps.Z}
\usepackage{stfloats}
\usepackage{float}
\usepackage{caption}
\begin{document}

\title{START: Status and Region Aware Taxi Mobility Model for Urban Vehicular Networks}

\author{\IEEEauthorblockN{Haiquan Wang\authorrefmark{1}\authorrefmark{2}\authorrefmark{3}, Wenjing Yang\authorrefmark{1}\authorrefmark{2}, Jingtao Zhang\authorrefmark{1}\authorrefmark{2}, Jiejie Zhao\authorrefmark{1}\authorrefmark{2}, Yu Wang\authorrefmark{3}\thanks{This research has been partially supported by the US National Science Foundation (NSF) under Grant No. CNS-1319915 and CNS-1343355, the National Natural Science Foundation of China (NSFC) under Grant No. 61300173, 61428203, and 61170295, the Project of Aeronautical Science Foundation of China under Grant No.2013ZC51026 and 2011ZC51024, the Fundamental Research Funds for the Central Universities under Grant No. YWF-12-LXGY-001, and the State Key Laboratory Software Development Environment and Network Information and Computing Center of Beihang University.}}
\IEEEauthorblockA{\authorrefmark{1}School of Software, Beihang University, Beijing, China\\
\authorrefmark{2}Beijing Key Laboratory of Network Technology, Beijing, China\\
\authorrefmark{3}Department of Computer Science, University of North Carolina at Charlotte, Charlotte, USA}}

\maketitle

\begin{abstract}
The mobility model in urban vehicular networks is one of the most important factors that impacts the evaluation of any vehicular networking protocols via simulations. However, to obtain a realistic mobility model in the dynamic urban environment is very challenging. Recently, several studies extract mobility models from large-scale real data sets (mostly taxi GPS data) without consideration of the statuses of taxi. In this paper, we discover two simple observations related to the taxi status via mining of real taxi traces: (1) the behavior of taxi will be influenced by the statuses, and (2) the macroscopic movement is related with different geographic features in corresponding status. Based on these two observations, a novel taxi mobility model (START) is proposed with respect to taxi status and geographic region. The simulation results illustrate that proposed mobility model has a good approximation with reality in trace samples, distribution of nodes and the contact characteristics.
\end{abstract}

\input{file_introduction}

%\input{file_related_works}

\section{Statistical Analysis of Beijing Taxi Traces}
\label{section_assumptions_anlysis}

In this section, we focus on the statistical analysis on the speed, duration, and taxi event characteristics of the Beijing taxi data set, a large-scale urban vehicular trace data.

\input{file_trace_dataset}

\subsection{Two Claims on Taxi Behaviors}
\label{section_statistic_analysis}

The following two claims are foundations of the proposed taxi mobility model, which are also reasonable based on the experience in our daily life:
\begin{itemize}
  \item \textbf{Claim 1:} The behavior of a taxi changes when its status updates. When a taxi is occupied, its destination is certain, and the vehicular speed of a occupied taxi accelerates relatively. In contrast, when a taxi is vacant, it slows down or even stops to search for potential passengers along the road. Therefore, taxi behavior characteristics, such as speed and status duration, vary consequently.

  \item \textbf{Claim 2:} The movement behavior of taxis associates with geographic features. When a taxi is occupied, the destination may be tend to certain geographic places, such as the airport. Meanwhile, when a taxi is vacant, its driver tends to look for some hot spots, where more people want to take a taxi, such as downtown areas. Therefore,
      \begin{enumerate}
        \item The destination selection of a taxi is influenced by different regions.
        \item Events occur in different regions un-evenly, passenger drop and load events are distinct.
      \end{enumerate}
\end{itemize}
Next, we analyze the speed, duration and passenger load/drop events distribution over the Beijing taxi traces to validate the two claims above.

\input{file_speed_statics}
\input{file_lasting_time_for_each_status}
\input{file_taxi_density_distribution}

\section{START Mobility Model}
\label{section_modeling}

\input{file_model_design}

\input{file_matrix_of_transition_probability}

\input{file_speed_modeling}

%\input{file_lasting_time_modeling}

\input{file_evaluation}

\section{Conclusion}
\label{section_conclusion}
Since the mobility model is important for vehicular networks and other smart cities applications, a new mobility model START based on real taxi GPS data is proposed. By assuming the taxi behavior is related with its statuses and geographic features, statistical experiments are conducted to verify those assumptions using the real trace data. With carefully estimations of the average speed distribution of each status and the region transition probability between drop and load event regions, START considers both macroscopic and microscopic movements. For the macroscopic movements, a node moves and switches between load-event regions and drop-event regions. Then the microscopic movements (such as speeds for each status) can be applied. START is implemented and evaluated in ONE simulator by comparing with the real trace, RWP and SP mobility models.
For both node distribution and contact features, START shows better performance than the other two mobility models. This demonstrates that START has a good approximation with reality and can be used for urban vehicular network research and applications.


%\bibliographystyle{IEEEtran}
%\bibliography{vehicle_mobility_model}

\begin{thebibliography}{10}

\bibitem{LuChen-104}
X.~Lu, Y.-c. Chen, I.~Leung, Z.~Xiong, and P.~Lio, ``A novel mobility model
  from a heterogeneous military MANET trace,'' in \emph{Proc. of 7th International Conference on Ad-hoc, Mobile and Wireless Networks (ADHOC-NOW)}, 2008.

\bibitem{AhmedKarmakar-106}
S.~Ahmed, G.~C. Karmakar, and J.~Kamruzzaman, ``An environment-aware mobility
  model for wireless ad hoc network,'' \emph{Computer Networks}, vol.~54,
  no.~9, pp. 1470--1489, 2010.

\bibitem{broch1998performance}
J.~Broch, D.~A. Maltz, D.~B. Johnson, Y.-C. Hu, and J.~Jetcheva, ``A
  performance comparison of multi-hop wireless ad hoc network routing
  protocols,'' in \emph{Proc. of the 4th annual ACM/IEEE international
  conference on Mobile computing and networking}, 1998.

\bibitem{SahaJohnson-91}
A.~K. Saha and D.~B. Johnson, ``Modeling mobility for vehicular ad-hoc
  networks,'' in \emph{Prox. of the 1st ACM International Workshop on
  Vehicular Ad Hoc Networks}, 2004.

\bibitem{MartinezCano-87}
F.~J. Martinez, J.-C. Cano, C.~T. Calafate, and P.~Manzoni, ``Citymob: a
  mobility model pattern generator for vanets,'' in \emph{Proc. of IEEE International Conf. on Communications Workshops}, 2008.

\bibitem{ChoffnesBustamante-93}
D.~R. Choffnes and F.~A. N.~E. Bustamante, ``An integrated mobility and traffic
  model for vehicular wireless networks,'' in \emph{Proc. of the 2nd ACM
  international workshop on Vehicular ad hoc networks}, 2005.

\bibitem{KimKotz-99}
M.~Kim, D.~Kotz, and S.~Kim, ``Extracting a mobility model from real user
  traces.'' in \emph{Proc. of 25th IEEE International Conference on
  Computer Communications (INFOCOM)}, 2006.

\bibitem{HuangZhu-88}
H.~Huang, Y.~Zhu, X.~Li, M.~Li, and M.-Y. Wu, ``Meta: A mobility model of
  metropolitan taxis extracted from gps traces,'' in \emph{Proc. of IEEE Wireless
  Communications and Networking Conference (WCNC)}, 2010.

\bibitem{Ganti}
R.~Ganti, M.~Srivatsa, A.~Ranganathan, and J.~Han, ``Inferring human mobility
  patterns from taxicab location traces,'' in \emph{Proc. of the ACM
  International Joint Conference on Pervasive and Ubiquitous Computing (UbiComp)}, 2013.

\bibitem{Aslam}
J.~Aslam, S.~Lim, X.~Pan, and D.~Rus, ``City-scale traffic estimation from a
  roving sensor network,'' in \emph{Proc. of the 10th ACM Conference on
  Embedded Network Sensor Systems (SenSys)}, 2012.

\bibitem{KeranenOtt-155}
A.~Keraen, J.~Ott, and T.~Karkkainen, ``The {ONE} simulator for {DTN} protocol
  evaluation,'' in \emph{Proc. of the 2nd International Conference on
  Simulation Tools and Techniques}, 2009.

\end{thebibliography}


%\input{file_clustering}
\end{document}
\endinput




